Exploring the linear separablity of syntactic and semantic information in BERT embeddings

### 2022-06-09 paper/paper.tex
fixed minor typos

\title{Proposal for Analyzing Language Models: Separatablity of Syntax and Semantics}

@@

To evaluate the separability of syntax and semantics, we use two task: one task for the probing system and INLP procedure, and one task for evaluating performance on embeddings before and after INLP. We choose Combinatory Categorical Grammar (CCG from here on) tagging \citep{ccg-bank} as the syntactic task and semantic category labeling \citep{propbank} as the semantic task.

@@

Similar to the above, the semantic probing tasks involves training a linear classifier on the final layer BERT embeddings in order to predict the semantic tag (described in the data section) associated with each word. This classifier is used in the INLP algorithm in order to create a guarding function, $P_{sem}$, for the information necessary to complete the Semantic tag labeling task. As described in the Syntactic probing task section, we shall use the resulting guarding function to decompose the original embedding into a ``non-semantic component'', $v_{no sem} = P_{sem} x$, and a ``semantic component'', $v_{sem} = x - v_{no sem}$.

>>>>

\title{Exploring the linear separablity of syntactic and semantic information in BERT embeddings }

@@

To evaluate the separability of syntax and semantics, we use two tasks: one task for the probing system and INLP procedure, and one task for evaluating performance on embeddings before and after INLP. We choose Combinatory Categorical Grammar (CCG from here on) tagging \citep{ccg-bank} as the syntactic task and semantic category labeling \citep{propbank} as the semantic task.

@@

Similar to the above, the semantic probing task involves training a linear classifier on the final layer BERT embeddings in order to predict the semantic tag (described in the data section) associated with each word. This classifier is used in the INLP algorithm in order to create a guarding function, $P_{sem}$, for the information necessary to complete the Semantic tag labeling task. As described in the Syntactic probing task section, we shall use the resulting guarding function to decompose the original embedding into a ``non-semantic component'', $v_{no sem} = P_{sem} x$, and a ``semantic component'', $v_{sem} = x - v_{no sem}$.
